A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-05-19 none_feedback_sequence_classifier/doc/main.tex
Adds figures

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

\begin{document}
% \nipsfinalcopy is no longer used

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
      \label{fig:path_alignment}
    }
\end{figure}

@@

In TFSC, we propose the following N-best alignment approach rather than
the Viterbi alignment algorithm to find the alignment information.

@@

  \Require {$\mathcal{X}_0^{M}$}
  \Require {$\mathcal{Y}_0^{L}$}

  \For {$m = 0, . . . , M-1$}
    \For {$l = 0, . . . , N_b-1$}
      \State {$\pi^{(l)}[m]$}
    \EndFor
  \EndFor

  \If {$i\geq maxval$}
      \State $i\gets 0$
  \Else
      \If {$i+k\leq maxval$}
          \State $i\gets i+k$
      \EndIf
  \EndIf
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{mathrsfs}
\usepackage{algpseudocode}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

\begin{document}

% \nipsfinalcopy is no longer used

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
      \label{fig:path_alignment}
    }
  \label{fig:path_alignment}
\end{figure}

@@

In FSC, we propose the following N-best alignment approach rather than
the Viterbi alignment algorithm to find the alignment information.

TODO(chanw.com) Define $f$.

@@

  \Require {$\vec{\mathcal{X}}[0:M]$}
  \Require {$\mathcal{\vec{Y}}_{0:L}$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ for calculating 
      $p\left(\vec{z}[m] \big|
      \mathcal{\vec{Z}}[0:m], \mathcal{\vec{X}}[0:m+1]\right)$}

  \State {\textbf{Initialization:}}
  \State {Let $\vec{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
  \State {$\vec{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
  \State {Let $\mathcal{L}_{0} := \ln \left[ 
        p \left(\vec{y}_{0} \big| 
            \vec{\mathcal{X}}[0:1]\right)  \right]$}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$\vec{\mathcal{Z}}_{b}[0:m]$ is defined}
        \State {Let $\vec{y}_u := \mathcal{\vec{Z}}_{b}[m-1] $}
        \State {Let $\vec{\mathcal{Z}}_{b, 0}[0:m+1] := \vec{\mathcal{Z}}_{b}[0:m] 
                \cup \left\{ \vec{y}_u  \right\}  $} 
            \Comment {A horizontal move $P \rightarrow Q$ in Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{L}_{b,0} := \ln \left[ 
                  p \left(\vec{y}_{u} \big| 
                      \vec{\mathcal{Z}}_b[0:m], 
                      \vec{\mathcal{X}}[0:m+1], \Theta^{(i)}\right)  \right]
                  + \mathcal{L}_b$}

        \If {$u+1 \le  L - 1$}
          \State {Let $\vec{\mathcal{Z}}_{b, 1}[0:m+1] := \vec{\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{L}_{b,1} := \ln \left[ 
                  p \left(\vec{y}_{u+1} \big| 
                      \vec{\mathcal{Z}}_b[0:m], \vec{\mathcal{X}}[0:m+1], \Theta^{(i)}\right)  \right] 
                          + \mathcal{L}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{L}_{b, i}, \vec{\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le b < B, i = 0, 1$ 
    with respect to the log likelihood $\left\{\mathcal{L}_{b, i}\right\}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{L}_{b}, \vec{\mathcal{Z}}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}
